04_DESeq_sexes_manipulate

### 2019-09-07 analysis/04_DESeq2_sexes_manipulate.Rmd
two to one
share prl module plots

# treatment
a <- LDAplot.manipulation(LDA.hyp1 , "Hypothalamus model 1", "parental state ~ .  0.277 pred. acc.",
                        "LD1, F = 7.1504779", "LD2, F = 2.4219585")

b <- LDAplot.manipulation(LDA.pit1 ,  "Pituitary model 1", "parental state ~ .  0.33 pred. acc.",
                        "LD1, F = 6.393554", "LD2, F = 3.396018")

c <- LDAplot.manipulation(LDA.gon1 , "Gonad model 1", "parental state ~ .  has 0.297 pred. acc.",
                        "LD1, F = 6.137500", "LD2, F = 3.320437")

@@

>>>>

# treatment
a <- LDAplot.manipulation(LDA.hyp1 , "Hypothalamus model 1", "parental state ~ .  0.185 pred. acc.",
                        "LD1, F = 3.7984170", "LD2, F = 3.0810558")

b <- LDAplot.manipulation(LDA.pit1 ,  "Pituitary model 1", "parental state ~ .  0.407 pred. acc.",
                        "LD1, F = 6.188592", "LD2, F = 3.604309")

c <- LDAplot.manipulation(LDA.gon1 , "Gonad model 1", "parental state ~ .  has 0.154 pred. acc.",
                        "LD1, F = 4.066997", "LD2, F = 2.782389")

@@

## genes that were in the WGCNA module with PRL twice!

```{r, sharedmodule}
PRL_associated <- read.csv("../results/08_PRL_associated.csv", header = T)
PRL_manipulated <- read.csv("../results/08_PRL_manipulated.csv", header = T)

str(PRL_associated)
str(PRL_manipulated)
PRLjoin <- inner_join(PRL_associated, PRL_manipulated, by = "entrezid")

PRLboth <- PRLjoin$entrezid
PRLboth

plotWGCNAcandidatesManip(vsd.pit, PRLboth, colDataPit, "PRL char and manip WGNA shared modules")

prl36 <-  PRL_manipulated$entrezid[252:271]
plotWGCNAcandidatesManip(vsd.pit, prl36, colDataPit, "A-K genes with PRL pattern in the pituitary")
